Digital History in Finland, 1488-1828

### 2016-07-11 inst/examples/manuscript-krakow.Rmd

>>>>

### Combining devotional literature and temporary sermons

```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=6}
sel <- c("virret","arkkiveisut","hartauskirjat","katekismukset","rukouspäivät","saarnat","aapiset","rukoukset","rukous","hengelliset laulut","hartauspuheet","virsikirjat","hautajaiset","häät","juhlamenot")
catalogue <- "Fennica"
  df <- df0 # selected time span
  df$hit <- apply((sapply(sel, function (x) {grepl(x, tolower(df$subject_topic))})), 1, any)

  # Selected catalogue with selected years
  df = filter(df0, catalog == catalogue & publication_year >= 1640 & publication_year <= 1828)

  lang <- paste("language.", langs, sep = "")
  otherlang <- setdiff(names(df)[grep("lang.", names(df))], lang)
  df$language.Other <- rowSums(df[, otherlang] == TRUE, na.rm = T) > 0
  dfl <- NULL
  for (lan in lang) {
    # Classify a document to the specifed language
    # If document is assigned with languages, each case is considered
    # so one doc may have multiple entries corresponding to different languages
    # mean(rowSums(df[, lang]) == 1) # 93% Fennica docs have just 1 language
    # Combine data frames for specified languages
    dflsub <- filter(df, df[[lan]])
    if (nrow(dflsub) > 0) {
      dflsub$language <- gsub("language.", "", lan)
      dfl <- bind_rows(dfl, dflsub)
    }
}

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       #geom_point(aes(col = language, shape = language), size = 5) +
       #geom_line(aes(col = language, shape = language)) +
       geom_bar(stat = "identity", aes(fill = language, )) +              
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
  print(p)
```
